---
title: "COVID 19 preLights"
output: html_notebook
---



```{r}
library(tidyverse)
library(shiny)
library(shinythemes)
library(RColorBrewer)
library(rtweet)
library(tidytext)
library(wordcloud2)
```````

````{r}
setwd("C:/Users/jonat/Desktop/COVID test")
``````

````{r}
# Process data from the shared google doc

read.csv("Data input.csv") -> Data 
head(Data)
colnames(Data)
names(Data)[names(Data) == "ï..Link"] <- "link"
head(Data, 10)
#Save the fixed data frame 
saveRDS(Data, "final_data.rds")

# Create table for extra info and label columns appropriately
info_table <- data.frame(Data$start,Data$content,Data$title, Data$summary)
names(info_table)[names(info_table) == "Data.start"] <- "Date"
names(info_table)[names(info_table) == "Data.content"] <- "Title"
names(info_table)[names(info_table) == "Data.title"] <- "further information"
names(info_table)[names(info_table) == "Data.summary"] <- "preprint summary"


# Run script by Lars and then add doi info to info table
info_table$link_if_published <- doi_links
# Save the info table
saveRDS(info_table, "infotable.rds")

# Resources table
read.csv("resources.csv") -> resources
names(resources)[names(resources) == "ï..Decription"] <- "Description"
head(resources)
saveRDS(resources, "resources.rds")


#Clean if necessary
#info_table[-c(108:119),] -> info_table

# Original upload
sinai_reviews <- list.files(path="./sinai",pattern="\\.md")
data.frame(sinai_reviews) -> "Sinai"

# Copy Sinai data frame into excel sheet "sinai fix" and then replace the sinai review text in app.R with the fixed file names

# Add extra rows without complete re-run of is published?
df <- read.delim("./book.txt")
names(df)[names(df) == "further.information"] <- "further information"
names(df)[names(df) == "preprint.summary"] <- "preprint summary"


df <- df %>% 
  select(1:5)

info_table <- rbind(info_table, df) 
````

````{R}
# Author: Lars Hubatsch
# Scraping is largely taken from a blog post of Paul Hook at
# https://pwh124.github.io/blog/2018/04/17/2018-03-18-scraping-biorxiv-part-2-navigating-javascript-in-r/
# Major difference in scraping: phantomjs is deprecated, now using firefox instead
# Good to know: trailing or leading white spaces in links can cause issues
# Returns: -1 if no link in column
#          -2 if link exists but cannot be assigned, this is for debugging
#           0 not published yet
#           1 published/peer-reviewed

library(RSelenium)
library(rvest)
library(magrittr)
library(readxl)

# Read xlsx file
sheet <- read.csv("./Data input.csv")

# Start browser session
driver<- rsDriver(browser="firefox")
# Sys.sleep(10) # Apparently not necessary
remDr <- driver[["client"]]
# remDr$open(silent = TRUE) # Also not necessary

x <- c()
doi_links <- c()

for (n in seq(1, nrow(sheet), 1)){
 if (is.na(sheet[n,1])){
   print("No link.")
   x[n] <- -1
 } else{
# Navigate to link, extract static AND dynamic content
remDr$navigate(toString(sheet[n,1]))
hlink <- remDr$getPageSource()[[1]] %>% read_html()

# Get the element that contains the journal
pub_string <- hlink %>%
  html_nodes(".pub_jnl") %>%
  html_text() %>%
  extract(1) %>%
  strsplit(" ") %>%
  unlist()

# Check whether published
if("preprint" %in% pub_string & "article" %in% pub_string){
  doi_links[n] <- "NA"
  x[n] <- 0
} else if ("Now" %in% pub_string & "published" %in% pub_string){
  pub_doi <- tail(unlist(strsplit(pub_string, " ")),1)
  x[n] <- 1
  doi_links[n] <- paste("https://doi.org/", pub_doi, sep = "")
} else{
  doi_links[n] <- "No preprint"
  x[n] <- -2
}
print(x)
}
}


# Close connections/stop browser
remDr$close()
driver[["server"]]$stop()

# Add doi info to sheet
#sheet$link <- doi_links

# Write dataframe with publishing status and dois to file
#write.csv(data.frame(x, doi_links), 'published.csv')
````









````{r}
# Check for new reviews from Sinai - not working yet!

# Original upload
sinai_reviews <- list.files(path="./Mount_Sinai_Reviews/covid-19_sinai_reviews/markdown_files",pattern="\\.md")
data.frame(sinai_reviews) -> "Sinai"

# Copy Sinai data frame into excel sheet "sinai fix" and then replace the sinai review text with the fixed file names

# Import updated list as new column - change "Sinai$update" each time  
Sinai$update <- list.files(path="./sinai",pattern="\\.md")
# Check for distinct entries 
Sinai %>% distinct()
```








```{r}
# Analysis of discussions on Twitter for #COVID19

# Set up twitter API access token
twitter_token <- create_token(
  app = ****,
  consumer_key = ****,
  consumer_secret = ****,
  set_renv = TRUE)

# Search recent tweets for "#COVID19" and create dataframe, not including retweets, returning 18,000 instances

covid_tweets <- search_tweets("#COVID19", n = 18000, include_rts = FALSE, lang = "en", type = "mixed")

# Organise by number of favs
covid_favs <- covid_tweets %>% arrange(-favorite_count)
#covid_favs[1,5]


# Clean text data for further analysis, removing specific words
covid_tweets$text <- gsub("https\\S*", "", covid_tweets$text)
covid_tweets$text <- gsub("@\\S*", "", covid_tweets$text) 
covid_tweets$text <- gsub("amp", "", covid_tweets$text) 
covid_tweets$text <- gsub("[\r\n]", "", covid_tweets$text)
covid_tweets$text <- gsub("[[:punct:]]", "", covid_tweets$text)
covid_tweets$text <- gsub("covid19", "", covid_tweets$text)
covid_tweets$text <- gsub("COVID19", "", covid_tweets$text)
covid_tweets$text <- gsub("Covid19", "", covid_tweets$text)


# Remove stop words and create document term matrix (words and frequencies)
tweets <- covid_tweets %>% 
  select(text) %>% 
  unnest_tokens(word, text)

tweets <- tweets %>% 
  anti_join(stop_words)

tweets_words <- tweets %>% count(word, sort = TRUE)
  
# Create document term metrix (words and frequencies)
#tweets_words <-  covid_tweets %>%
 #select(text) %>%
 #unnest_tokens(word, text)

#tweets_words <- tweets_words %>% count(word, sort=TRUE)

# Create in wordcloud2 (Save by running the below in the console then saving from viewer pane)
wordcloud2(tweets_words, color = "random-dark")

#letterCloud(tweets_words, word = "COVID19", wordSize = 5) 

# Play with data


# Who is tweeting the most about #COVID19?
length(unique(covid_tweets$screen_name))

covid_tweets %>% 
  count(screen_name, sort = TRUE) %>%
   mutate(screen_name = reorder(screen_name, n)) %>% 
  top_n(20) %>% 
  ggplot(aes(x = screen_name, y = n)) +
  geom_col() + 
  coord_flip() +
  labs(x = "Name", y = "count", title = "Source of tweets")

# Sentiment analysis of the processed text content. N.b lexicon has a bias towards negative words
library(syuzhet)

# Converting tweets to ASCII to trackle strange characters
Sentiment_table <- iconv(tweets, from="UTF-8", to="ASCII", sub="")

ew_sentiment <- get_nrc_sentiment((Sentiment_table))

sentimentscores <- data.frame(colSums(ew_sentiment[,])) 

names(sentimentscores) <- "Score"

sentimentscores <- cbind("sentiment"=rownames(sentimentscores),sentimentscores)

rownames(sentimentscores) <- NULL

ggplot(data=sentimentscores,aes(x=sentiment,y=Score)) +
  geom_bar(aes(fill=sentiment),stat = "identity") +
  theme(legend.position="none") +
  xlab("Sentiments") +ylab("Scores") +
  ggtitle("Total sentiment based on scores")+
  theme_minimal()





# Random sample of tweets, timeout is in seconds 

rt <- stream_tweets(lang = "en", timeout = 30)

rt <- search_tweets("", n = 10000, include_rts = FALSE, lang = "en", type = "mixed")

rt$text <- gsub("https\\S*", "", rt$text)
rt$text <- gsub("@\\S*", "", rt$text) 
rt$text <- gsub("amp", "", rt$text) 
rt$text <- gsub("[\r\n]", "", rt$text)
rt$text <- gsub("[[:punct:]]", "", rt$text)

random_tweets <- rt %>% 
  select(text) %>% 
  unnest_tokens(word, text)

random_tweets <- random_tweets %>% 
  anti_join(stop_words)

random_tweets_words <- random_tweets %>% count(word, sort = TRUE)

wordcloud2(random_tweets_words, color = "random-dark")


Sentiment_table2 <- iconv(random_tweets, from="UTF-8", to="ASCII", sub="")

ew_sentiment2 <- get_nrc_sentiment((Sentiment_table2))

sentimentscores2 <- data.frame(colSums(ew_sentiment2[,])) 

names(sentimentscores2) <- "Score"

sentimentscores2 <- cbind("sentiment"=rownames(sentimentscores2),sentimentscores2)

rownames(sentimentscores2) <- NULL

ggplot(data=sentimentscores2,aes(x=sentiment,y=Score)) +
  geom_bar(aes(fill=sentiment),stat = "identity") +
  theme(legend.position="none") +
  xlab("Sentiments") +ylab("Scores") +
  ggtitle("Total sentiment based on scores")+
  theme_minimal()
```











````{r}
timevis(Data, showZoom = TRUE, fit = TRUE)
``````

`````````{r}
#Shiny output for Timeline with colour & additional details- working
shinyApp(
  ui = fluidPage(
    
    titlePanel("Preprints in response to COVID-19, maintained by the @preLights team"),
    
    tags$style(
       ".event { background: darksalmon; }
      .preprint { background: deepskyblue; }
      .bad { background: moccasin; }"
    ),
    timevisOutput("timeline"),
  
     #Add buttons to allow user to control view
     actionButton("btn", "Fit all items"),
   actionButton("btn2", "Center on first reported case"),
   
   #Add rows underneath containing additional text
   br(),
   br(),

  fluidRow(
    column(2,
      h4(" ")),
    h3("Key: Red = Event, Blue = Preprint, Orange = Important caveat/comment on preprint")),
    
    br(),
   
  fluidRow(
        column(3,
          tableOutput('info_table')
        )),
  
  br(),
  
  
   fluidRow(
    column(2,
      h4("PreLights team")),
    br(),
    # Add a hyperlink 
    p("List of contributors and ", 
      a("link.", 
          href = "http://shiny.rstudio.com"))),
 
   br(), 
   
  fluidRow(
    column(2,
      h4("Authors et al / preprint title")),
    br(),
    p("Paragraph of text.")),
  
  img(src = "prelights.png", height = 70, width = 200),
  
  fluidRow(
    column(2,
      h4("")),
    br(),
    p("preLights is a community service supported by The Company of Biologists, the not-for-profit publisher of Development, Journal of Cell Science, Journal of Experimental Biology, Disease Models & Mechanisms and Biology Open. The Company of Biologists is also a UK charity, providing grants and other support for the scientific community. 
Follow preLights on Twitter at https://twitter.com/preLights"))
  
  ),
  
  server <- function(input, output, session) {
  output$timeline <- renderTimevis({
    timevis(Data)
  })
  
  output$table <- renderTable(info_table)
  
#Make buttons work
    observeEvent(input$btn, {
      fitWindow("timeline", list(animation = TRUE))
    })
     observeEvent(input$btn2, {
      centerItem("timeline", 1, (animation = TRUE))
    })
  }
)  
`````````

```{r}
#Working shiny applet with no colours
ui <- fluidPage(
  timevisOutput("timeline")
)
server <- function(input, output, session) {
  output$timeline <- renderTimevis({
    timevis(Data)
  })
}
shinyApp(ui = ui, server = server)
````



`````{R}
#Other timevis example things
  timevis(
       data.frame(id = 1:2,
                  content = c("one", "two"),
                  start = c("2016-01-10", "2016-01-14"),
                  end = c(NA, "2016-01-18"),
                  type = c("point", "box"))
     )

#help(timevis)
```


```{r}
# Testing


#Import data
readRDS("final_data.rds") -> final_data
readRDS("infotable.rds") -> info_table
readRDS("resources.rds") -> resources


#Import markdown files from Mount Sinai
#?

#Define UI
shinyApp(
  ui = navbarPage("Preprints & COVID-19",
                  theme = shinytheme("spacelab"),
                  tabPanel("Timeline",
                           fluidPage(
                             
                             titlePanel("Landmark preprints in response to COVID-19, maintained by the @preLights team"),
                             
                             tags$style(
                               ".event { background: darksalmon; }
      .preprint { background: darkturquoise; }
      .bad { background: moccasin; }"
                             ),
                             timevisOutput("timeline"),
                             
                             #Add buttons to allow user to control view
                             actionButton("btn", "Fit all items"),
                             actionButton("btn2", "Center on first reported case"),
                             actionButton("btn3", "Center on 1st Feb"),
                             actionButton("btn4", "Center on 1st March"),
                             actionButton("btn5", "Center on 1st April"),
                             actionButton("btn6", "Center on 1st May"),
                             
                             #Add rows underneath containing additional text
                             br(),
                             br(),
                             
                             fluidRow(
                               column(2,
                                      h4(" ")),
                               h3("Key: Orange = Event, Teal = Preprint, yellow = Important caveat/comment on preprint (see further information). Last updated: 01/04/2020")),
                             
                             #br(),
                             
                             fluidRow(
                               column(2,
                                      h4("")),
                               br(),
                               h3("This work is being maintained by Gautam Dey, Srivats Venkataramanan, Sundar Naganathan, Debbie Ho, Zhang-He Goh, Kirsty Hooper, Lars Hubatsch, Mariana De Niz, Sejal Davla, Mate Palfy & Jonny Coates. For questions or queries please contact prelights@biologists.com or Jonny Coates jc2216@cam.ac.uk")),
                             
                             br(),
                             
                             fluidRow(
                               column(2,
                                      h4("")),
                               h4("To use the timeline, navigate by clicking and dragging or through the use of the buttons. Hovering the mouse over an item will reveal more details pertaining to that point. Navigate between the timeline view and the table view using the navigation buttons at the top of this page. This timeline will be updated weekly.")),
                           
                             br(),
                             
                             img(src = "prelights.png", height = 70, width = 200),
                             
                             fluidRow(
                               column(2,
                                      h4("")),
                               p("preLights is a community service supported by The Company of Biologists, the not-for-profit publisher of Development, Journal of Cell Science, Journal of Experimental Biology, Disease Models & Mechanisms and Biology Open. The Company of Biologists is also a UK charity, providing grants and other support for the scientific community. 
                                 Follow preLights on Twitter at https://twitter.com/preLights"))
                           )),
                  
                  
                  
                  
                  # Page 2
                  
                  tabPanel("Further information",
                           DT::dataTableOutput("table")
                  ),
                  
                  # Page 3
                  tabPanel("Resources",
                           DT::dataTableOutput("resources")
                  ),
                  
                  # Page 4 - About
                  tabPanel("About",
                           fluidRow(
                             column(2,
                                    h4("")),
                             br(),
                             h3("We'd like to thank the tremendous effort of our team who are maintaining this database (twitter handles): Gautam Dey (@Dey_Gautam), Srivats Venkataramanan (@srivatsv), Sundar Naganathan (@Sundar_Ram_07), Debbie Ho, Zhang-He Goh (@zhanghe_goh), Kirsty Hooper (@KirstyHooper13), Lars Hubatsch (@LarsHubatsch), Mariana De Niz (@mariana_deniz), Sejal Davla (@JustABrainThing), Mate Palfy (@mate_palfy) & Jonny Coates (@JACoates91). In addition, our thanks go out to the wider scientific community who are diligently assessing and communicating important preprints during this difficult time. For questions or queries please contact prelights@biologists.com  or Jonny Coates jc2216@cam.ac.uk"),
                             br(),
                             h3("Please also find a curated prelist of interesting COVID-19 related preprints ",
                             a("here ", 
                               href = "https://prelights.biologists.com/prelists/wuhan-coronavirus-2019-ncov/"),
                             ("or visit the preLights website "),
                             a("here.",
                               href = "https://prelights.biologists.com")),
                             br(),
                             h3("The underlying code and data in support of this resource can be found on ",
                                a("github.",
                                  href = "https://github.com/coatesj/shiny-server"))),
                           
                           br(),
                           
                           fluidRow(
                             column(2,
                                    h4("")),
                             p("preLights is a community service supported by The Company of Biologists, the not-for-profit publisher of Development, Journal of Cell Science, Journal of Experimental Biology, Disease Models & Mechanisms and Biology Open. The Company of Biologists is also a UK charity, providing grants and other support for the scientific community. 
                                 Follow preLights on Twitter at https://twitter.com/preLights")),
                           br(),
                           
                           img(src = "prelights.png", height = 70, width = 200)),
                           
      # Page 5, manually load Sinai review .md files
      tabPanel("Mount Sinai peer-reviews of COVID-19 preprints",
                           fluidRow(
                             column(2, 
                                    h4("")),
                             br(),
                             h3("The following is a collection of the Mount Sinai Immunology researchers (@MountSinaiNYC). We thank the team for their important efforts in reviewing critical literature during such a turbulent period and for allowing us to link to these reviews. See https://observablehq.com/@ismms-himc/covid-19-sars-cov-2-preprints-from-medrxiv-and-biorxiv for more."),
                             br(),
      includeMarkdown("./sinai/10.1101-2020.01.28.923011.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.03.20020289v2.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.03.931766.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.05.20020545.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.07.939389.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.08.20021212.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.08.939553.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.08.939892.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.10.20021584.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.10.20021832v1.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.11.20022053.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.12.20022418.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.12.945576.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.16.20023671.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.16.20023903.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.16.951723.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.17.951939.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.18.20024364.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.19.20025239.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.19.20025288.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.19.955484.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.19.95658.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.20.20025841.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.23.20026690.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.25.20024711.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.25.20025643.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.25.963546v3.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.25.965434v2.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.26.20026989.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.27.20029009v2.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.28.20028514.md"),br(),
includeMarkdown("./sinai/10.1101-2020.02.29.20029520.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.01.20029074.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.01.20029769.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.01.20029785.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.02.20029975.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.03.20030437.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.03.20030668.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.03.962332.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.04.20030395.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.04.20030916.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.04.20031120.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.05.20031906.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.05.979260.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.06.20031856.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.08.20031229.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.09.20033068.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.11.20031096.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.11.987016.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.11.987958v1.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.12.20035048.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.13.990226.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.13.991570.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.14.20036129.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.14.988345.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.15.20033472.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.15.993097.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.16.20036145.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.16.20037135.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.16.990317.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.17.20037713.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.17.995639.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.18.20038018.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.18.20038059.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.18.20038190.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.18.20038455.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.19.20038315.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.20.999730.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.21.001628.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.21.20040261.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.21.20040691.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.21.990770.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.22.002204v1.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.22.002386.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.22.20040758.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.004655.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.20042119.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.20042283.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.20042382.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.20042655.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.24.20042937.md"),br(),
includeMarkdown("./sinai/10.1101-2020.03.28.013672.md"),br(),
includeMarkdown("./sinai/10.11012020.02.03.20020206.md"),br()

                           ))
                  # Close UI
  ),
  
  
  # Server settings  
  server <- function(input, output, session) {
    output$timeline <- renderTimevis({
      timevis(final_data, fit = FALSE)
    })
    
    output$table <- DT::renderDataTable({
      DT::datatable(info_table, list(lengthMenu = c(10, 25, 30, 50, 75, 100), pageLength = 50))
    })
    
    output$resources <- DT::renderDataTable({
      DT::datatable(resources, list(lengthMenu = c(5, 10, 15, 20), pageLength = 10))
    })
    
    #Make buttons work
    observeEvent(input$btn, {
      fitWindow("timeline", list(animation = TRUE))
    })
    observeEvent(input$btn2, {
      centerItem("timeline", 1, (animation = TRUE))
    })
    observeEvent(input$btn3, {
      centerTime("timeline", "02-01-2020", (animation = TRUE))
    })
    observeEvent(input$btn4, {
      centerTime("timeline", "03-01-2020", (animation = TRUE))
    })
    observeEvent(input$btn5, {
      centerTime("timeline", "04-01-2020", (animation = TRUE))
    })
    observeEvent(input$btn6, {
      centerTime("timeline", "05-01-2020", (animation = TRUE))
    })
  }
)
```